Article Analysis Notebook

### 2017-10-26 Article analysis notebook.Rmd
where did the summary go?

@@

#Step 1. Load packages and data
Before I run any parts of the analysis, I load all the packages I use in this file
```{r load libraries}
require(dplyr)
require(ggplot2)
require(stringr)
require(plotrix) #to calculate standard error
```
First in excel, I deleted two rows of non-table data, i.e. title, and a note, and saved the file (S2_Table) as a CSV in the project directory. Then I read it into R and converted it to a table using dplyr. I trimed white space at beginnings and ends of things where there shouldn't be any, and kept strings as is to avoid issues later down the line. 
```{r readfile arch}
iso_total<-read.csv("S2_Table.csv", header=TRUE, stringsAsFactors = FALSE, strip.white=TRUE)
iso_total<-tbl_df(iso_total)
head(iso_total)
str(iso_total)
```
```{r readfile modern}
modern<-read.csv("S1_Table.csv", header=TRUE, skip=3, strip.white=TRUE, stringsAsFactors = FALSE) #here I used skip=3 to skip the first 3 rows before the data started
modern<-tbl_df(modern)
head(modern)
str(modern)
```

>>>>

First I modified the files slightly to import with curl, as it refused to bring in the header names with certain symbols in (it worked fine importing from local repo).

@@

#Step 1. Load packages and data
Before I run any parts of the analysis, I load all the packages I use in this file
```{r load libraries}
require(dplyr)
require(ggplot2)
require(stringr)
require(plotrix) #to calculate standard error
require(qwraps2)
```
First in excel, I deleted two rows of non-table data, i.e. title, and a note, and saved the file (S2_Table) as a CSV in the project directory. Then I read it into R and converted it to a table using dplyr. I trimed white space at beginnings and ends of things where there shouldn't be any, and kept strings as is to avoid issues later down the line. 
```{r readfile arch}
library(curl)
f <- curl("https://raw.githubusercontent.com/mazattack/Article-analysis/master/S2_Table.csv")
iso_total <- read.csv(f, header = TRUE, stringsAsFactors = FALSE, strip.white=TRUE)
iso_total<-tbl_df(iso_total)
head(iso_total)
str(iso_total)
```
```{r readfile modern}
f <- curl("https://raw.githubusercontent.com/mazattack/Article-analysis/master/S1_Table.csv")
modern<-read.csv(f, header=TRUE, sep = ",", skip=0, strip.white=TRUE, stringsAsFactors = FALSE) #here I used skip=3 to skip the first 3 rows before the data started
modern<-tbl_df(modern)
head(modern)
str(modern)
```
